---
title: "p8105_hw1_xw2758"
author: "Xinyi Wang"
date: 2020-09-15
output: github_document
---

This is my solution to HW1!

```{r}
library(tidyverse)
library(ggplot2)
```

## Problem 1

Create a data frame with the specific element.

```{r}
prob1_df <- 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("high", "low", "low", "low", "low", "low", "low", "med", "med", "med"))
)
```

Take the mean of each variable in my data frame.

```{r, mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

**I can take the mean of numbers and logical but not character or factor.**

```{r, try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r, convert_numeric_multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```


## problem 2

**First, I load the dataset!**

```{r}
data("penguins", package = "palmerpenguins")
```

**Then, I give a short discription of penguins dataset.**

(1) I find this dataset has `r ncol(penguins)` different variables, including `r names(penguins)`. 
     - `r names(penguins[,1])`'s value is `r levels(pull(penguins,species))`.
     - `r names(penguins[,2])`'s value is `r levels(pull(penguins,island))`.
     - `r names(penguins[,3])`'s range is `r range(pull(penguins,bill_length_mm), na.rm = TRUE)`.
     - `r names(penguins[,4])`'s range is `r range(pull(penguins,bill_depth_mm), na.rm = TRUE)`.
     - `r names(penguins[,5])`'s range is `r range(pull(penguins,flipper_length_mm), na.rm = TRUE)`.
     - `r names(penguins[,6])`'s range is `r range(pull(penguins,body_mass_g), na.rm = TRUE)`.
     - `r names(penguins[,7])`'s value is `r levels(pull(penguins,sex))`.
     - `r names(penguins[,8])`'s range is `r range(pull(penguins,year))`.
(2) It has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
(3) The mean of flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.


**Then, I show a scatterplot of flipper_length_mm (y) vs bill_length_mm (x).**

```{r scatterplot}
gen_plot = ggplot(
  penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species),
)+ geom_point(na.rm = TRUE)
```

**Finally, I will save the scatterplot!**

```{r, save_plot}
ggsave("gen_plot.pdf")
```



